A Spatial AR System for Wide-area Axis-aligned Metric Augmentation of Planar Scenes

### 2021-07-24 paper/elsarticle/elsarticle-template.tex
paper

%% Group authors per affiliation:
\author{Michael Horn\'{a}\v{c}ek}\corref{mycorrespondingauthor}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{michael.hornacek@tuwien.ac.at}
\author{Hans K\"{u}ffner-McCauley}
\author{Majesa Trimmel}
\author{Patrick Rupprecht}
\author{Sebastian~Schlund}
\address{Human Centered Cyber Physical Production and Assembly Systems, Institute for Management Sciences, TU Wien, Vienna, Austria}

@@

One way to compute a homography is by identifying at least four correspondences between pixel positions in two images of a planar surface. The keystone correction approach of Sukthankar \etal \cite{sukthankar2001smarter} reduces to using a segmentation approach to identify the four corners of projection screen in an image acquired by a camera, and computing a homography that maps the resulting four corners of the projection screen to the four corners of the projector's image plane. Tilt sensors can be used to recover the projector's gravity vector, and be integrated in the computation of a homography as in Raskar and Beardsley \cite{raskar2001self}.

@@

Calibration of a projector (or camera) in the sense we employ the term here\footnote{We are referring to a geometric calibration; not, e.g., to a color calibration.} renders one able to project a scene point~$\mathbf{X} \in \mathbb{R}^3$ to its corresponding pixel~$\mathbf{x} \in \mathbb{R}^2$ in the projector's (or camera's) image plane, or to compute the `back-projection' of $\mathbf{x}$, i.e., the ray from the projector's (or camera's) center of projection through $\mathbf{x}$ along which $\mathbf{X}$ must lie. Such a calibration can be expressed in terms of (i) a $3~\times{}~3$ calibration matrix~$\mathtt{K}$ derived from the projector's (or camera's) focal length and principal point \cite{Hartley2004}, and (ii) the coefficients of a lens distortion model used to correct for radial or tangential distortions caused by the lens system \cite{duane1971close}.

In practice, calibrating a camera relies on (i) establishing 2D-3D correspondences between pixels in the camera's image plane and corresponding points in the scene, and on (ii) using those correspondences as input to an optimization procedure that relies on bundle adjustment \cite{triggs1999bundle} to output the calibration matrix~$\mathtt{K}$, the associated lens distortion model coefficients, and, for each calibration image, the pose (i.e., position and orientation) of the camera relative to the 3D points \cite{Hartley2004,zhang2000flexible}. To calibrate a camera, images of a calibration surface such as a chessboard pattern are used to identify the 2D-3D correspondences $\{\mathbf{x}_{i,j} \leftrightarrow \mathbf{X}_{i,j}\}$, $i \in \{ 1, \dots, n_\text{pt} \}, j \in \{ 1, \dots, n_\text{im} \}$, where $n_\text{pt}$ gives the number of correspondences obtained from one calibration image of the pattern, $n_\text{im}$ the number of such images, and $\mathbf{X}_{i,j} = \mathbf{X}_{i,j'}$, for $j, j' \in \{ 1, \dots, n_\text{im} \}$. Bundle adjustment is used to obtain the lens distortion model coefficients, calibration matrix~$\mathtt{K}$, and rigid body transformations $(\mathtt{R}_j, \mathbf{t}_j) \in SE(3)$ that minimize the reprojection error
\begin{equation}
\sum_{i,j} d\big(\mathbf{x}_{i,j}, \mathtt{K}(\mathtt{R}_j\mathbf{X}_{i,j} + \mathbf{t}_j)\big),
\label{re}
\end{equation}
where $\mathbf{X}_{i,j}' = \mathtt{R}_j\mathbf{X}_{i,j} + \mathbf{t}_j$ expresses $\mathbf{X}_{i,j}$ in the camera coordinate frame corresponding to the $j^{\text{th}}$ calibration image, $\mathtt{K}\mathbf{X}_{i,j}' \in \mathbb{R}^2$ gives the projection of $\mathbf{X}_{i,j}$ to that image, and $d$ is a distance function that corrects for lens distortion using the recovered lens distortion model coefficients and computes a distance with respect to the two undistorted pixel positions. The inverse rigid body transformation~$(\mathtt{R}_j^{-1}, -\mathtt{R}_j^{-1}\mathbf{t}_j^{})$ gives the pose of the $j^{\text{th}}$ camera relative to the 3D points of the calibration pattern.

>>>>

%% Group authors per affiliation:
\author{Michael Horn\'{a}\v{c}ek}\corref{mycorrespondingauthor}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{michael.hornacek@tuwien.ac.at}
\author{Hans K\"{u}ffner-McCauley}
\author{Majesa Trimmel}
\author{Patrick Rupprecht}
\author{Sebastian Schlund}
\address{Human Centered Cyber Physical Production and Assembly Systems, Institute for Management Sciences, TU Wien, Vienna, Austria}

@@

One way to compute a homography is by identifying at least four correspondences between pixel positions in two images of a planar surface. The keystone correction approach of Sukthankar \textit{et al.} \cite{sukthankar2001smarter} reduces to using a segmentation approach to identify the four corners of projection screen in an image acquired by a camera, and computing a homography that maps the resulting four corners of the projection screen to the four corners of the projector's image plane. Tilt sensors can be used to recover the projector's gravity vector, and be integrated in the computation of a homography as in Raskar and Beardsley \cite{raskar2001self}.

@@

Calibration of a projector (or camera) in the sense we employ the term here\footnote{We are referring to a geometric calibration; not, e.g., to a color calibration.} renders one able to project a scene point~$\mathbf{X} \in \mathbb{R}^3$ to its corresponding pixel~$\mathbf{x} \in \mathbb{R}^2$ in the projector's (or camera's) image plane, or to compute the `back-projection' of $\mathbf{x}$, i.e., the ray from the projector's (or camera's) center of projection through $\mathbf{x}$ along which $\mathbf{X}$ must lie. Such a calibration can be expressed in terms of (i) a $3~\times{}~3$ calibration matrix~$\mathtt{K}$ derived from the projector's (or camera's) focal length~$f$ and principal point~$\mathbf{p}_0 = (x_0, y_0)^\top \in \mathbb{R}^2$ \cite{Hartley2004}, and (ii) the coefficients of a lens distortion model used to correct for radial or tangential distortions caused by the lens system \cite{duane1971close}; the calibration matrix~$\mathtt{K}$ is then
\begin{equation}
\mathtt{K} = \begin{bmatrix}
f & 0 & x_0 \\
0 & f & y_0 \\
0 & 0 & 1
\end{bmatrix},
\end{equation}
where $f$ and $(p_x, p_y)^\top$ are both expressed in units of pixels.

In practice, calibrating a camera relies on (i) establishing 2D-3D correspondences between pixels in the camera's image plane and corresponding points in the scene, and on (ii) using those correspondences as input to an optimization procedure that relies on bundle adjustment \cite{triggs1999bundle} to output the calibration matrix~$\mathtt{K}$, the associated lens distortion model coefficients, and, for each calibration image, the pose (i.e., position and orientation) of the camera relative to the 3D points \cite{Hartley2004,zhang2000flexible}. To calibrate a camera, images of a calibration surface such as a chessboard pattern are used to identify the 2D-3D correspondences~$\{\mathbf{x}_{i,j} \leftrightarrow \mathbf{X}_{i,j}\}$, $i \in \{ 1, \dots, n_\text{pt} \}, j \in \{ 1, \dots, n_\text{im} \}$, where $n_\text{pt}$ gives the number of correspondences obtained from one calibration image of the pattern, $n_\text{im}$ the number of such images, and $\mathbf{X}_{i,j} = \mathbf{X}_{i,j'}$, for $j, j' \in \{ 1, \dots, n_\text{im} \}$. Bundle adjustment is used to obtain the lens distortion model coefficients, calibration matrix~$\mathtt{K}$, and rigid body transformations $(\mathtt{R}_j, \mathbf{t}_j) \in SE(3)$ that minimize the reprojection error
\begin{equation}
\sum_{i,j} d\big(\mathbf{x}_{i,j}, \mathtt{K}(\mathtt{R}_j\mathbf{X}_{i,j} + \mathbf{t}_j)\big),
\label{re}
\end{equation}
where $\mathbf{X}_{i,j}' = \mathtt{R}_j\mathbf{X}_{i,j} + \mathbf{t}_j \in \mathbb{R}^3$ expresses $\mathbf{X}_{i,j}$ in the camera coordinate frame of the camera corresponding to the $j^{\text{th}}$ calibration image, $(\mathbf{x}_{i,j}', 1)^\top \sim \mathtt{K}\mathbf{X}_{i,j}' \in \mathbb{P}^2$ gives the projection~$\mathbf{x}'_{i,j} \in \mathbb{R}^2$ of $\mathbf{X}_{i,j}'$ to that image, and $d$ is a distance function that~(i) corrects for lens distortion using the recovered lens distortion model coefficients~\cite{duane1971close} and (ii) returns a distance with respect to the two undistorted pixel positions. The inverse rigid body transformation~$(\mathtt{R}_j^{-1}, -\mathtt{R}_j^{-1}\mathbf{t}_j^{})$ gives the pose of the $j^{\text{th}}$~camera relative to the 3D points of the calibration pattern.
